---
title: "Event summary"
author: "Bird Count India"
date: "`r Sys.Date()`"
output: word_document
editor_options: 
  chunk_output_type: console
---

```{r setup, include=FALSE}

knitr::opts_chunk$set(echo = FALSE)


library(curl)
library(tidyverse)
library(lubridate)
library(glue)
library(writexl)
library(rebird)
# library(skimmr)

# Get an eBird API token and assign it to object myebirdtoken
source("token.R")
source("scripts/functions.R")


ebd <- read_csv("eBirdTaxonomy.csv")
# soib <- read_csv("../soib-v2/01_analyses_full/results/SoIB_main.csv")


# get required dates, admin units (MAKE MODIFICATIONS HERE)
get_dates(seq(as_date("2022-11-04"), as_date("2022-11-07"), by = "days"))
cur_region <- get_admin_codes("IN-NL", hi_arch = FALSE)
cur_region_children <- get_admin_codes(cur_region, hi_arch = TRUE)

```

```{r data-processing, include=FALSE}

# species lists & participation summaries
spec_list_main <- gen_spec_list(cur_region, dates_cur)
part_summ_main <- gen_part_summ(cur_region, dates_cur)

spec_list_sub <- gen_spec_list(cur_region_children, dates_cur) %>% 
  filter(REGION != cur_region)
part_summ_sub <- gen_part_summ(cur_region_children, dates_cur) %>% 
  filter(REGION != cur_region)

```

[Paragraph about event intro, coincidence with global event if so]

**1507 birdwatchers** from India came together and documented **873 species** in **5,460 checklists**! Participants represented **34 states/union territories**(, provinces, and districts). 81 new eBirders participated in this event. In addition to this, [**2,458 photos** and **113 sound recordings**](https://media.ebird.org/catalog?mediaType=photo&sort=rating_rank_desc&obsDtFrom=2023-10-14&obsDtTo=2023-10-14&regionCode=IN) were uploaded to the Macaulay Library!

[Placeholder for nice ML image]

Thanks to all birdwatchers and nature enthusiasts from across the country who made this event a success. A special shout out to all those who took this opportunity to conduct public bird walks and introduce new people to the wonders of birds and nature!

Table 1: Total number of lists uploaded from states/ union territories

Table 2: Total number of species reported from states/ union territories

[Placeholder for birding image]

**Note:** This is just a summary and the final results will be published end of November 2023

Thank you to everyone for interacting with the public and students, organising bird walks and talks, and promoting the joy of birdwatching!